Articles_Plots

### 2022-10-03 Articles.Rmd
plots are updated for visibility

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average MSE Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average MSE Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6

>>>>

Theme_special<-function()
{
  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-1,-2,-1,-2)) 
}

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average MSE of Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Average MSE of Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6
